### 2017-03-06 draft-md-ct.tex
quick fix (clarification) added

Continuing as in \cite[Section 5]{Kwon-M}.
Consider the discrete-time updates
\begin{align*}
y_{t+1} &= y_{t} - \eta v_{t}\,, \label{eq.dta.1} \tag{1dt'} \\
x_{t+1} &= \nabla R^{*}(y_{t+1})\,. \label{eq.dta.2} \tag{2dt'}
\end{align*}
These are the discrete-time counterparts of \eqref{eq.cta.1}--\eqref{eq.cta.2} form
the previous section. As in \cite{Kwon-M}, let's start by embedding the discrete-time process
$(v_{t})_{t \geq 0}$ into a continuous-time stream $v(t)$ by setting
\begin{equation}
v(t) = v_{\lceil t \rceil},\hspace{7mm} t \in [0,\infty)\,.
\label{eq.dt.to.ct.embed}
\end{equation}
We will derive a regret bound for the strategy \eqref{eq.dta.1}--\eqref{eq.dta.2}.
The bound will consist of a term coming form the continuous time analysis of the previous section 
applied to the continuous stream \eqref{eq.dt.to.ct.embed}, 
plus a term accounting for a comparison between the discrete and continuous time processes.

@@

Assume we have a $K$-strongly convex regularizer $R$.
Denoting as before $x(t) = \nabla R^{*} (y(t))$ and $y(t) = \eta \int_{0}^{t} v(s) ds$,
we have
$$
x_{t} = \nabla R^{*} \Bigl( \eta \sum_{k=1}^{t-1} v_{k} \Bigr) = x(t-1).
$$
Note that $x_t$ on the left is the value of the discrete-time process at stage $t$,
while $x(t-1)$ in the right is the continuous-time process at time $t-1$.

@@

Now, for a fixed arbitrary $x$, we get
\begin{align*}
\sum_{k=1}^{t} \ab{v_{k},x}
= \int_{0}^{t} \ab{v(s), x} ds 
&\leq \int_{0}^{t} \ab{v(s), x(s)} ds + \frac{R_{\text{max}} - R_{\text{min}}}{\eta} \\
&\leq \sum_{k=1}^{t} \ab{v_{k},x_{k}} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2 
     + \frac{R_{\text{max}} - R_{\text{min}}}{\eta}\,.
\end{align*}
The first inequality is from \eqref{eq.cta.bound} \todoc{Why can this be applied?
Does $(x(t),y(t))_{t}$ satisfy \eqref{eq.cta.1}--\eqref{eq.cta.2}? Any other conditions?}
and the second inequality
from the above continuous/discrete time comparison for the linearized losses.
Finally, using linearization of the original losses (in discrete time) we get
\begin{align*}
\sum_{k=1}^{t} \ell_{k}(x_{k}) - \sum_{k=1}^{t} \ell_{k}(x)
&\leq \sum_{k=1}^{t} \ab{v_{k},x - x_{k}} \\
&\leq \frac{R_{\text{max}} - R_{\text{min}}}{\eta} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2\,.
\end{align*}

>>>>

Continuing as in \cite[Section 5]{Kwon-M}.
Consider the discrete-time updates
\begin{align*}
y_{t+1} &= y_{t} - \eta v_{t}\,, \label{eq.dta.1} \tag{1dt'} \\
x_{t+1} &= \nabla R^{*}(y_{t+1})\,. \label{eq.dta.2} \tag{2dt'}
\end{align*}
These are the discrete-time counterparts of \eqref{eq.cta.1}--\eqref{eq.cta.2} form
the previous section. As in \cite{Kwon-M}, let's start by embedding the discrete-time process
$(v_{t})_{t \geq 0}$ into a continuous-time stream $v(t)$ by setting
\begin{equation}
v(t) = v_{\lceil t \rceil},\hspace{7mm} t \in [0,\infty)\,.
\label{eq.dt.to.ct.embed}
\end{equation}
Based on the continuous-time stream $v(t)$ we define
$y(t) = \eta \int_{0}^{t} v(s) ds$ 
and $x(t) = \nabla R^{*} (y(t))$. \todoo{$(x(t),y(t))$ defined from $(x_{t},y_{t})$.}
Then by construction $x(t)$ and $y(t)$ satisfy \eqref{eq.cta.1}--\eqref{eq.cta.2}.
When $t = k$ is an integer, we have 
$y(t) = \eta \int_{0}^{t} v(s) ds = \eta \sum_{j=1}^{k} v_{j} = y_{k+1}$,
so then $y(t) - y(t-1) = y_{k+1} - y_{k} = -\eta v_{k}$
and $x(t) = \nabla R^{*} (y(t)) = \nabla R^{*} (y_{k+1})$.
The pair $(x(t),y(t))$ \todoo{makes sense?}
satisfies \eqref{eq.dta.1}--\eqref{eq.dta.2} at integer times $t$.

@@

We will derive a regret bound for the strategy \eqref{eq.dta.1}--\eqref{eq.dta.2}.
The bound will consist of a term coming form the continuous time analysis of the previous section 
applied to the continuous stream \eqref{eq.dt.to.ct.embed}, 
plus a term accounting for a comparison between the discrete and continuous time processes.

Assume $R$ is a $K$-strongly convex regularizer.
%Denoting as before $x(t) = \nabla R^{*} (y(t))$ and $y(t) = \eta \int_{0}^{t} v(s) ds$,
We have
$$
x_{t} = \nabla R^{*} \Bigl( \eta \sum_{k=1}^{t-1} v_{k} \Bigr) = x(t-1).
$$
Note that $x_t$ on the left is the value of the discrete-time process at stage $t$,
while $x(t-1)$ in the right is the continuous-time process at time $t-1$.

@@

Now, for a fixed arbitrary $x$, we get
\begin{align*}
\sum_{k=1}^{t} \ab{v_{k},x}
= \int_{0}^{t} \ab{v(s), x} ds 
&\leq \int_{0}^{t} \ab{v(s), x(s)} ds + \frac{R_{\text{max}} - R_{\text{min}}}{\eta} \\
&\leq \sum_{k=1}^{t} \ab{v_{k},x_{k}} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2 
     + \frac{R_{\text{max}} - R_{\text{min}}}{\eta}\,.
\end{align*}
The first inequality is from \eqref{eq.cta.bound} \todoc{Why can this be applied?
Does $(x(t),y(t))_{t}$ satisfy \eqref{eq.cta.1}--\eqref{eq.cta.2}? Any other conditions?}
and the second inequality
from the above continuous/discrete time comparison for the linearized losses.
Finally, using linearization of the original losses (in discrete time) we get
\begin{align*}
\sum_{k=1}^{t} \ell_{k}(x_{k}) - \sum_{k=1}^{t} \ell_{k}(x)
\leq \sum_{k=1}^{t} \ab{v_{k},x - x_{k}} 
\leq \frac{R_{\text{max}} - R_{\text{min}}}{\eta} + \frac{\eta}{2K} \sum_{k=1}^{t} \norm{v_{k}}_{*}^2\,.
\end{align*}
